Titeln på avhandlingens språk

### 2022-08-23 model.tex
explaining

\section{A model of human behavior for \ac{WCA}}\label{sec:model}

In order to accurately emulate the behavior of a human, a model for \ac{WCA} needs to implement two main behaviors.
One, it needs to generate realistic \emph{execution times} for each step in the task, considering the current and historical impairment of the \ac{WCA} system.
And two, it needs to produce sequences of video frames for each step which mimic what a human generate.
\todo[inline]{Improve}

In this section, we present and discuss our approaches to both these challenges.

@@

>>>>

\section{A model of human behavior for \acl*{WCA}}\label{sec:model}

In~\cite{olguinmunoz:impact2021} we studied the effects of system responsiveness on human behavior in step-based \ac{WCA} through human-subject trials.
We employed a modified and instrumented version of the LEGO Assistant application devised by~\textcite{Chen2015LEGO}, which belongs to a category of \acp{WCA} with the goal of guiding a user through a sequential task.
The application monitors the progress of the task in ``realtime'' by repeatedly sampling the state of the physical system, most commonly through video frames.
Whenever the applications detects that the user has correctly or incorrectly performed an instruction, it provides a new instruction to either advance the task or correct the detected mistake.
Subjects interacted with this \ac{WCA} while the responsiveness of the system was altered in realtime and we captured key application and task performance metrics.
Additionally, we also employed questionnaires to evaluate key personality traits of the participants, and correlated these results to the task performance metrics collected.

From this experimentation, we identified four main results concerning the step execution times of humans in \ac{WCA}:

In the following, we employ the above insights together with the actual data collected for~\cite{olguinmunoz:impact2021} to design and build a probabilistic model of human behavior for \ac{WCA}.
In order to accurately emulate the behavior of a human, such a model for needs to implement two main behaviors.
One, it needs to generate realistic \emph{execution times} for each step in the task, considering the current and historical impairment of the \ac{WCA} system.
And two, it needs to produce sequences of video frames for each step which mimic what a human generate.

@@

We begin by providing some formal definitions relating to step-based \acl{WCA}.
\begin{description}
    \item[Task:] understood as a finite sequence of instructions to be executed in order.
    \item[Step:] specific action to be performed by the user, described by a single instruction; e.g. put a green $1 \times 3$ brick on the board.
    \item[Step duration:] the time interval between 
    \item[Step execution time:]
    \item[Wait time:]
    \item[\ac{TTF}:]   
\end{description}

The step starts at \(t_0\), when the instruction is presented to the user.
We call the interval \(t_c - t_0\) the ``execution time'', corresponding to the time the user takes to complete the instruction.
The final sample of the step is taken at \(t_n\) and it takes \( t_{n+1} - t_n \) time units for the user to receive a reply from the backend (``last sample \ac{RTT}'').
Finally, we call the time interval between when the user finishes the instruction and the capturing of the final sample the ``wait time''; together with the last sample \ac{RTT} it composes the ``Time-to-Feedback'' of the step.%

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/task.png}
        \caption{%
            Overview of a task in a \ac{WCA}, composed of a series of steps.
            Each steps starts with an instruction being provided to the user and ends with the instruction for the next step.
            The \ac{WCA} continuously samples the task state, automatically triggering transitions between steps as correct (or incorrect) states are recognized.
        }\label{}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/step_time.png}
        \caption{%
            Breakdown of a step into its timing components.
            The instruction for step \( M \) and \( M + 1 \) are provided to the user at \( t_0 \) and \( t_{n+1} \), respectively.
            \( t_k | k \in \{1, \ldots, n \} \) correspond to the \ac{WCA} sampling instants for step \( M \), and \( t_c \) marks the instant at which the user finishes performing the instruction.
        }\label{}
    \end{subfigure}
    \caption{}
\end{figure}

A task will be understood as a finite sequence of instructions to be performed in order. Step will refer to a specific action to be performed by the user, described by a single instruction; e.g. put a green 1 × 3 brick on the board (see Fig 2). A step starts with an instruction being given to the user, and ends when the assistant detects that the user has finished performing it. At that point, the assistant either provides a new instruction to the user, or the task ends.
